Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-25 paper/zhang-cook-laa-langrene-menendez.Rmd
clean up the toy tour view and vimeo

```{r toy-pca-animated, fig.cap = "A selected number of frames from the animated PCA plots. With animation, it is easier to track the progression of each optimiser from the start to finish. A full video of the aimation can be found at \\url{https://vimeo.com/user132007430/review/504242845/b73f37175a}"}
```

@@

```{r toy-tour, fig.cap="A selected number of frames from the tour animation for viewing the 5D space of all the projection bases. The second frame on the top row views the space from a direction that is close to the one in the PCA plot. The tour animation allows for a more holistic view of the full space in high dimensions from different angles."}
```

>>>>

```{r toy-pca-animated, fig.cap = "A selected number of frames from the animated PCA plots. With animation, it is easier to track the progression of each optimiser from the start to finish. A full video of this aimation can be found at \\url{https://vimeo.com/user132007430/review/504242845/b73f37175a}"}
```

@@

```{r toy-tour, fig.cap="A selected number of frames from the tour animation for viewing the 5D space of all the projection bases. The tour animation allows for a more holistic view of the full space in high dimensions from different angles. A full video of this aimation can be found at \\url{https://vimeo.com/user132007430/review/504328122/9be84db563}"}
```

### 2021-01-25 paper/zhang-cook-laa-langrene-menendez.tex
clean up the toy tour view and vimeo

\caption{A selected number of frames from the animated PCA plots. With animation, it is easier to track the progression of each optimiser from the start to finish. A full video of the aimation can be found at \url{https://vimeo.com/user132007430/review/504242845/b73f37175a}}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}

@@

\caption[A selected number of frames from the tour animation for viewing the 5D space of all the projection bases]{A selected number of frames from the tour animation for viewing the 5D space of all the projection bases. The second frame on the top row views the space from a direction that is close to the one in the PCA plot. The tour animation allows for a more holistic view of the full space in high dimensions from different angles.}\label{fig:toy-tour}
\end{figure}
\end{Schunk}

>>>>

\caption{A selected number of frames from the animated PCA plots. With animation, it is easier to track the progression of each optimiser from the start to finish. A full video of this aimation can be found at \url{https://vimeo.com/user132007430/review/504242845/b73f37175a}}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}

@@

\caption{A selected number of frames from the tour animation for viewing the 5D space of all the projection bases. The tour animation allows for a more holistic view of the full space in high dimensions from different angles. A full video of this aimation can be found at \url{https://vimeo.com/user132007430/review/504328122/9be84db563}}\label{fig:toy-tour}
\end{figure}
\end{Schunk}
